---
title: "Wrangling Exercise"
author: "Naema Ahmed"
date: "9/20/2016"
output: html_document
---

```{r download, echo=FALSE}
library(dplyr)
library(magrittr)
library(nycflights13)
data(flights)
```

1.Filter flights to include only flights with an arrival delay greater than 2 hours (delays are recorded in minutes)
```{r q1}
head(flights %>% filter(arr_delay > 120))
```

2.Select columns in the flights table that contain delay times (note that the function matches can be used to select columns with names that matches a regular expression. See ?dplyr::select)

```{r q2}
head(select(flights, matches("delay")))
```

3.Find the minimum arrival delay (this can be a negative number) in the flights table. Use summarize.
```{r q3}
flights %>% summarize(min_arrival_delay = min(arr_delay, na.rm=TRUE))
```

4.Find minimum arrival delay (again, can be a negative number) in the flights table for each destination airport. Use group_by' and 'summarize.
```{r q4}
head(flights %>%
  group_by(dest) %>% 
  summarize(min_arrival_delay = min(arr_delay, na.rm=TRUE)))
```

5.List the name of all airlines and the number of flights for each airline in flights table. The airlines table has airline names.
```{r q5}
head(flights %>%
  group_by(carrier) %>%
  summarize(total_flights = n()) %>%
  select(carrier, total_flights))
```

(a): create a new column (use ‘mutate’) with total delay time for each flight
```{r q5a}
head(new_table <-flights %>%
  mutate(total_delay = dep_delay + arr_delay) %>%
  select(total_delay))
```

(b): replace any missing total delay times with the average total delay time of the remiaining flights.
```{r q5b}
head(flights %>%
  mutate(total_delay = dep_delay + arr_delay) %>%
  mutate(mean_delay = mean(total_delay,na.rm=TRUE)) %>%
  mutate(fixed_total_delay = ifelse(is.na(total_delay), mean_delay, total_delay)) %>%
  select(total_delay,fixed_total_delay))
```
